\section{Proof and Accounting Appendix}

This appendix records the exact completion standard for the internal theory
draft.  A target result in the main text becomes a formal proposition only
after the corresponding item below contains assumptions, a complete
derivation, and boundary cases.

\subsection{Consumer-access block}

\begin{enumerate}
  \item Derive the channel demands, $s_P'(z)>0$, and $P_M'(z)<0$ from the CES
  expenditure problem.
  \item State the admissible parameter region and the limit cases
  $s_P\rightarrow0$ and $s_P\rightarrow1$.
\end{enumerate}

\subsection{Comparative-advantage definitions}

\begin{enumerate}
  \item Derive local factor opportunity costs from the background sector and
  regional endowments.
  \item Show how changes in the relevant endowment ratio affect
  $\mathcal C^P_{ij}$ for industries with different factor intensities.
  \item Keep \LCA, \ACA, viability, and realized comparative advantage
  distinct throughout the derivation.
\end{enumerate}

\subsection{Entry, organization, and local-income thresholds}

\begin{enumerate}
  \item Solve the producer's entry problem and derive $G_E^*$.
  \item Solve the $P$--$L$ producer-organization choice and derive the
  conditions for $G_L^*$ or $M_L^*$.
  \item Keep consumer channel $A$ distinct from producer organization $L$.
  \item Construct one complete payment-flow table for channels $A$ and $P$,
  local producer sales, and the local/external components of complementary
  services.
  \item Verify that organizational choice changes both local service income
  and external payments; otherwise remove it from the baseline.
  \item Derive the monotonicity and boundary conditions required for a unique
  $G_Y^*$.
  \item Derive $G_R^*$ and prove $G_R^*<G_Y^*$ when both thresholds are
  interior.
  \item Report parameter regions in which either threshold does not exist or
  lies outside the feasible support.
\end{enumerate}

\subsection{Companion-paper mapping}

The final appendix must reproduce the exact income-propagation equation used
in the companion paper and provide a one-to-one map between:
\begin{enumerate}
  \item its autonomous-income term and the producer-side payments derived
  here;
  \item its local-retention denominator and the transaction set used here;
  \item its consumer price index and $P_M(z)$;
  \item its nominal and consumption-equivalent income definitions and
  $(Y_i,R_i)$ here.
\end{enumerate}
This check is required to rule out double counting of local production,
transaction services, and induced household spending.

\subsection{Policy and robustness}

The policy proof must state the market failure, government budget, real
resource cost, and incidence of any platform or local-service payment.  It
must also identify whether the intervention relaxes a constraint on
comparative-advantage realization, organizational embeddedness, or both.
Robustness work is limited to partial localization of platform-service income
and multiple candidate industries unless an additional mechanism changes one
of the core threshold results.
