\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

\newcommand{\LCA}{\ensuremath{\mathrm{LCA}}}
\newcommand{\ACA}{\ensuremath{\mathrm{ACA}}}

\title{When Does Market Access Become Local Development?\\
Platform Integration, Comparative-Advantage Realization,\\
and Local Value Capture}
\author{}
\date{Internal Theory-Architecture Draft --- July 2026}

\begin{document}

\maketitle

\begin{abstract}
Platform integration can lower local consumer prices while shifting trade away
from locally embedded channels.  It also gives local producers access to a
larger market, but that opportunity need not become local production and
income.  This paper asks when these two sides of platform integration jointly
produce local development.  Its theoretical object is the access--capture
problem developed in a companion short paper.  New Structural Economics
supplies the structural backbone on the local-development side: endowments
shape latent comparative advantage; hard and soft infrastructure determine
actual comparative advantage and firm viability; and organizational
embeddedness determines whether production and complementary-service payments
remain local.  The model therefore separates consumer access, producer access,
local channel displacement, comparative-advantage realization, and local
capture formation.  Its target results are
distinct thresholds for nominal local income and consumption-equivalent real
income, with the latter strictly lower because consumers benefit from the
price decline even when first-round local receipts fall.  Public facilitation
addresses an explicit shared-infrastructure or coordination failure in an
\LCA-consistent activity.  This internal draft fixes the paper's theoretical
architecture; proposition statements are not claims of proof until the
corresponding derivations are completed in the appendix.
\end{abstract}

\section{Introduction}

A common market does not connect every region to the national economy in the
same way.  Platform integration can make goods produced elsewhere cheaper and
more accessible to local consumers.  At the same time, it can displace local
wholesale, retail, logistics, and transaction services.  For local producers,
the same platform can enlarge the potential customer base.  Whether that
producer-side opportunity becomes local output, employment, service income,
and profits depends on the region's production structure and the transaction
conditions under which its firms operate.

The paper asks:
\begin{quote}
Why does platform-enabled market integration broadly improve consumer access,
yet translate into local production and income only when a region's latent
comparative advantage can be realized through appropriate local organization
and infrastructure?
\end{quote}

This formulation fixes the division of labor between the paper's two
theoretical components.  The access--capture problem is the object to be
explained.  New Structural Economics (NSE) provides the local structural
block: it disciplines industry choice, the conversion from latent to actual
comparative advantage, firm viability, organizational embeddedness, local
linkages, and the facilitating-state boundary.  The platform block supplies
the market-access and channel-substitution shocks, while the companion paper
supplies the income-propagation block.  The paper is therefore neither a
general theory of structural transformation with a platform added at the end
nor a version of the companion model in which ``local capability'' is simply
renamed comparative advantage.

The intended contribution has three parts.  First, consumer-side and
producer-side market access are modeled separately, even though both improve
with platform integration.  Second, local value capture is derived from the
location and ownership of production and transaction-service payments, rather
than imposed as a regional parameter; production and local complementary
services are jointly generated by the NSE block.  Third, the paper connects
the NSE distinction among latent comparative advantage, actual comparative
advantage, viability, and realization to the companion paper's distinction
between nominal local income and consumption-equivalent real income.

\section{The Access--Capture Benchmark}

\subsection{Consumer access and channel substitution}

Consider one focal region embedded in a larger national market.  A
representative local household consumes a channel-composite good supplied
through a locally embedded channel $A$ and an external platform channel $P$:
\[
 C_M=
 \left[
 a_A^{1/\eta}C_A^{(\eta-1)/\eta}
 a_P^{1/\eta}C_P^{(\eta-1)/\eta}
 \right]^{\eta/(\eta-1)},
 \qquad \eta>1.
\]
The associated price index and platform expenditure share are
\[
 P_M(z)=
 \left[
 a_Ap_A^{\,1-\eta}
 a_Pp_P(z)^{\,1-\eta}
 \right]^{1/(1-\eta)}
\]
and
\[
 s_P(z)=
 \frac{a_Pp_P(z)^{\,1-\eta}}
 {a_Ap_A^{\,1-\eta}+a_Pp_P(z)^{\,1-\eta}}.
\]
Platform integration is indexed by $z$ and satisfies $p_P'(z)<0$.  Hence
\[
 s_P'(z)>0,
 \qquad
 P_M'(z)<0.
\]
This block establishes a consumer-access gain and a shift in transaction
organization.  It does not, by itself, determine whether local firms can sell
to the national market.

\subsection{Payment location}

Let $\ell_A$ and $\ell_P$ denote the locally received value generated by one
unit of expenditure through the two channels.  They are accounting outcomes,
not independent behavioral parameters.  Each is constructed from mutually
exclusive payments to commodity producers, wholesale and retail services,
logistics and fulfilment services, platform services, and locally owned
profits.  In the benchmark case,
\[
 \ell_A>\ell_P,
\]
because a larger share of the traditional channel's transaction services is
locally provided, whereas platform fees and part of the platform's
organizational services accrue outside the focal region.

For a fixed first-round expenditure base $X_i$, the local transaction-service
component is
\[
 V_i^{\mathrm{channel}}(z)
 =
 X_i\left[
 \bigl(1-s_P(z)\bigr)\ell_A+s_P(z)\ell_P
 \right].
\]
Thus channel substitution can lower local receipts even while it lowers the
consumer price index.  This is the benchmark capture loss that the
production-side model must offset; it is not the paper's final result.

\section{Endowments and Latent Comparative Advantage}

\subsection{Production costs}

Region $i$ has endowment vector $E_i=(K_i,L_i)$.  A competitive background
sector $0$ anchors local opportunity costs $(w_i,r_i)$.  Candidate industry
$j$ has factor intensity $\theta_j$ and unit production cost
\[
 c^P_{ij}=c_j(w_i,r_i;\theta_j).
\]
The superscript $P$ identifies production cost before industry-specific
transaction costs.  This distinction is essential: NSE does not define
comparative advantage as the inverse of a single industry's absolute cost.

\subsection{Strict relative-cost definition}

Let $h$ be an external reference region and let $0$ be the internal benchmark
industry.  Define the production-cost comparison
\[
 \mathcal C^P_{ij}
 =
 \frac{c^P_{ij}/c^P_{i0}}
      {c^P_{hj}/c^P_{h0}}.
\]
Region $i$ has latent comparative advantage (\LCA) in industry $j$ when
\[
 \mathcal C^P_{ij}<1.
\]
This is a double-relative production-cost statement.  It says that, before
industry-specific transaction costs and infrastructure constraints, industry
$j$ is relatively better suited to region $i$ than to the reference region.
It does not imply that firms in $i$ can profitably produce and sell the good
under the existing business environment.

For clarity, the paper maintains four distinct concepts:
\begin{center}
\begin{tabular}{p{0.22\textwidth}p{0.68\textwidth}}
\toprule
Concept & Meaning in the model \\
\midrule
\LCA & Relative production-cost advantage implied by endowments and sectoral
factor intensities, before industry-specific transaction constraints. \\
\ACA & Relative total-cost advantage after the prevailing hard and soft
infrastructure, transaction costs, and organizational environment are taken
into account. \\
Viability & A firm's ability to cover actual production, transaction, and
fixed costs without permanent protection. \\
Realized comparative advantage & The equilibrium manifestation of
comparative advantage through viable entry, production, and sales.  It is an
outcome, not an alternative name for \LCA. \\
\bottomrule
\end{tabular}
\end{center}

\section{The NSE Structural Block}

\subsection{Producer access, comparative advantage, and viability}

Let $M(z)$ measure the national demand accessible to a local producer, with
$M'(z)>0$.  Channel $r$ entails transaction cost $t_{ijr}(G_i)$ and fixed
entry or organizational cost $f_{ijr}(G_i)$, where $G_i$ is a parsimonious
measure of the relevant shared infrastructure.  The total unit cost is
\[
 c^T_{ijr}
 =
 c^P_{ij}+t_{ijr}(G_i),
\]
and operating profit can be written as
\[
 \pi_{ijr}(z,G_i)
 =
 M(z)b_j\!\left(c^T_{ijr}\right)-f_{ijr}(G_i),
 \qquad b_j'(\cdot)<0.
\]
The firm enters the national market if
\[
 \max_r\pi_{ijr}(z,G_i)\geq0.
\]
This condition converts the potential represented by \LCA into an actual
producer response.  It also shows why \LCA, \ACA, viability, and realized
comparative advantage cannot be collapsed into one index.  \LCA is a relative
production-cost statement; \ACA incorporates the prevailing transaction
environment; viability requires the firm to cover its actual costs without
persistent protection; and entry is the equilibrium realization of these
conditions.

\subsection{Organizational embeddedness and local linkages}

On the producer side, an entrant chooses between external platform
organization $P$ and locally embedded organization $L$.  The locally embedded
consumer channel $A$ in the previous section is not a third producer-side
organization.  The choice is
\[
 r_{ij}^*
 \in
 \arg\max_{r\in\{P,L\}}
 \left\{0,\pi_{ijr}(z,G_i)\right\}.
\]
Mode $P$ uses marketing, settlement, fulfilment, or supply-chain services
provided outside the focal region.  Mode $L$ obtains the corresponding
services from local providers.  For each mode, the same service bill is
decomposed as
\[
 H_{ijr}
 =
 H_{ijr}^{\mathrm{local}}
 +
 H_{ijr}^{\mathrm{external}}.
\]
The first component enters local service income and the second is an external
payment.  Consequently, organizational embeddedness is not an independent
retention parameter: it is the payment-incidence consequence of the firm's
profit-maximizing organization.

In this baseline, local linkages mean only that complementary services
required by the candidate industry and its platform sales are supplied
locally.  They do not introduce endogenous supplier varieties, agglomeration
externalities, or cumulative causation.

\subsection{Why infrastructure is in the model}

$G_i$ is introduced only for infrastructure or organizational services with
a specific economic role: they reduce a transaction or fixed cost that a
potentially viable industry faces when reaching the integrated market.  In the
policy section, public provision is permitted only if this input is shared,
indivisible, coordination-intensive, or otherwise not fully internalized by a
single entrant.  Generic ``capacity'' that directly raises local retention is
not admissible.

\subsubsection*{Target result 1a: Comparative-advantage realization}
Under monotonicity and single-crossing conditions, there is an infrastructure
threshold
\[
 G_E^*=G_E^*(\mathcal C^P_{ij},M)
\]
above which a local firm enters.  Stronger \LCA should reduce the infrastructure
required for entry.  The result must be derived from the profit condition,
rather than imposed through an increasing capability function.

\subsubsection*{Target result 1b: Organizational embeddedness}
If local organization has a higher fixed cost but lowers the relevant
variable service cost or external payment, the profit difference
\[
 \Delta\pi_{ij}^{L-P}
 =
 \pi_{ijL}-\pi_{ijP}
\]
can generate an organizational-embedding threshold $G_L^*$ or $M_L^*$.
This result enters the baseline only if crossing the threshold changes
$H_{ijr}^{\mathrm{local}}$, $H_{ijr}^{\mathrm{external}}$, and therefore the
nominal or real local-income threshold.

\section{Local Value Capture and Income}

\subsection{First-round local income}

For one common set of transactions, first-round local income is
\[
 V_i
 =
 W_i^{\mathrm{local}}
 +\Pi_i^{\mathrm{local}}
 +S_i^{\mathrm{local}}
 +T_i^{\mathrm{local}}
 -C_i^{\mathrm{policy}}.
\]
The components are local labor income, locally owned net operating surplus,
local transaction-service value added, net local fiscal receipts when policy
is present, and the real resource cost of policy.  Each payment appears once.
The corresponding local retention share is
\[
 \omega_i
 =
 \frac{V_i}
 {\text{transaction value generated by the same transaction set}}.
\]

The change induced by platform integration is organized as
\[
\begin{aligned}
 \Delta V_i
 ={}&
 \Delta V_i^{\mathrm{producer}}
 +\Delta V_i^{\mathrm{local\ services}}\\
 &-\Delta V_i^{\mathrm{agent\ displacement}}
 -\Delta V_i^{\mathrm{external\ payments}}.
\end{aligned}
\]
The four terms respectively capture local entry, output, and outward sales;
locally supplied platform complements; the loss of locally embedded channel
services; and payments to the platform and outside organizational services.
The NSE structural block generates the first term through viability and entry,
and the second and fourth terms through organizational choice and service
payment incidence.  Only local-agent displacement is generated entirely by
the consumer-side channel-substitution block.  The substantive NSE extension
therefore concerns both production and the local organizational structure
through which transaction value is captured.

\subsection{The companion-paper income block}

The access--capture companion paper provides a conditional local-income
propagation block.  Denote its exact mapping by
\[
 Y_i=\mathcal M_i(\omega_i)V_i.
\]
The final version will substitute the companion paper's exact fixed-point
formula after matching the transaction denominator and avoiding double
counting of producer and service payments.  Consumption-equivalent local
income is
\[
 R_i=\frac{Y_i}{P_M(z)^\alpha},
\]
so that
\[
 \frac{d\ln R_i}{dz}
 =
 \frac{d\ln Y_i}{dz}
 -
 \alpha\frac{d\ln P_M(z)}{dz}.
\]
The propagation block amplifies the first-round local-income consequence.  It
does not replace the production-side entry problem, and it must not be added
as a second demand feedback inside the firm's resource constraint.

\section{Target Equilibrium Results}

\subsubsection*{Target result 2: Nominal local-income threshold}
The model must derive a unique $G_Y^*$ satisfying
\[
 \frac{dY_i}{dz}\geq0
 \quad\Longleftrightarrow\quad
 G_i\geq G_Y^*.
\]
Economically, infrastructure and \LCA jointly determine whether producer and
local-linkage gains offset local-agent displacement and external platform
payments.  NSE affects both the positive production margin and the spatial
incidence of complementary-service payments.

\subsubsection*{Target result 3: Real-income threshold}
The consumer price decline implies a distinct threshold $G_R^*$ satisfying
\[
 \frac{dR_i}{dz}\geq0
 \quad\Longleftrightarrow\quad
 G_i\geq G_R^*.
\]
When both thresholds are interior, the target ordering is
\[
 G_R^*<G_Y^*.
\]
This ordering generates three economically distinct regions:
\[
\begin{cases}
G_i<G_R^*: &
\text{nominal and consumption-equivalent local income both fall},\\[3pt]
G_R^*\leq G_i<G_Y^*: &
\text{nominal local income falls but the price gain raises real income},\\[3pt]
G_i\geq G_Y^*: &
\text{production and local-linkage gains make both measures rise}.
\end{cases}
\]
Stronger \LCA should lower both thresholds because a given improvement in
producer access and infrastructure induces a larger viable supply response and
can support locally embedded complementary services.  This statement requires
an increasing-differences or equivalent single-crossing condition; it cannot
be inferred merely by relabeling local capability.

\section{The Facilitating State}

The facilitating state is conceptually central to the NSE block but
analytically downstream of the positive equilibrium results.  Public action is
justified only when potentially viable firms in an \LCA-consistent industry
cannot individually supply a shared input or coordinate complementary
investments.  Facilitation then lowers a real fixed or transaction cost:
\[
 f_{ijr}'(G_i)<0
 \quad\text{or}\quad
 t_{ijr}'(G_i)<0,
\]
at a convex resource cost to the local economy.

This intervention differs from protection.  Facilitation improves the
region's ability to realize a production-cost advantage and, where relevant,
to form locally embedded complementary services.  Protection raises the
relative cost of the outside channel or shields firms that may not be viable.
The model does not assume that every infrastructure project is beneficial or
that facilitation always dominates every temporary support instrument.  The
policy result is conditional on three elements: an independently defined
\LCA, an explicit market failure preventing comparative-advantage realization
or organizational embeddedness, and benefits that exceed the policy's real
resource cost.

\section{Scope and Extensions}

The baseline deliberately excludes endogenous migration, agglomeration
externalities, endogenous national market size, dynamic organizational
capital, platform price setting, and a full multi-region general equilibrium.
These mechanisms are not required to answer the access--capture question.
New Economic Geography becomes relevant only in a later paper if endogenous
firm location and market size produce cumulative causation, multiplicity, or
path dependence.

The baseline retains only the minimal $P$--$L$ comparison required to
endogenize local-service and external-payment incidence.  An earlier model
contract studied three full producer-side thresholds: entry through an
external platform, stand-alone profitability of a local organizational
system, and switching from the platform to that system.  The complete
three-threshold structure may be restored as an extension only if it changes
$G_Y^*$ or $G_R^*$ without introducing an additional state variable.

\section{Conclusion}

The paper's fixed subject is not the general formation of comparative
advantage.  It is the local development incidence of platform-enabled market
integration.  NSE provides the local structural backbone: endowments determine
latent comparative advantage; the actual infrastructure and transaction
environment determine \ACA and viability; and organizational embeddedness
determines whether complementary-service payments remain local.  Combined
with the consumer price effect, local-channel displacement, and the
companion-paper income block, this mechanism can explain why equalized access
coexists with unequal local capture.

\appendix
\input{appendix}

\end{document}
